---
title: "R Notebook"
output: html_notebook
---

# BARB API Demo: The audiences by time endpoint

In this demo of the audiences by time endpoint we will:

1. Gain access to the API by requesting an access token
2. Query the API, requesting audience sizes for live viewing for BBC 1 on 15th Oct
3. Reshape the data into a pandas dataframe
4. Use the data to explore how different age groups watch the station at different times of day and how this varies by region.

## Set up the R environment

```{r}
library(tidyverse) ; library(httr) ; library(jsonlite); library(dplyr)
```

## Get the access token

This code uses your account details (store them in json format in the file `creds.json`) to get an access token from the API

```{r}
data <-fromJSON("creds.json")
link<-"https://barb-api.co.uk/api/v1/auth/token/"
r<-httr::POST(url = link,
           body =  jsonlite::toJSON(data, pretty = T, auto_unbox = T),
           httr::add_headers(`accept` = 'application/json'), 
           httr::content_type('application/json'))
access_token<-httr::content(r)$access
```

## Get data from the API

The access token is then used to query the API.

```{r}
head <-list("Authorization" = paste0("Bearer ", access_token))
auth_string = paste0("Bearer ", access_token)
api_url <- "https://barb-api.co.uk/api/v1/audiences_by_time/"
params <- list("min_transmission_date"="2022-10-25","max_transmission_date"="2022-10-25",
          "time_period_length"=15,"viewing_status"="live", "station_code"=10)
r<-httr::GET(url = api_url,
           query =  params,
           httr::add_headers(accept = 'application/json', Authorization = auth_string))
api_data<-httr::content(r)
```

How many events have been returned?

```{r}
length(api_data$events)
```

Note if there had been over 5000 events (the limit for a single API call) we would have needed to make several calls to the API using the x_next attribute.

## Reshape the data as a pandas dataframe

We now restructure the data as a dataframe. The json data is highly flexible. We are choosing the parts of the data that we need and turning them into a table.


```{r}
event_extraction <- function(item) {
  av <- item$audience_views
  audience_code<-sapply(av, function(x) {x$audience_code})
  size_in_hundreds<-sapply(av, function(x) {x$audience_size_hundreds})
  audience_views <- data.frame(audience_code, size_in_hundreds)
  audience_views$panel_region <- item$panel$panel_region
  audience_views$transmission_time_period <- item$transmission_time_period_start$standard_datetime
  return(audience_views)
}
bbc_1<-lapply(api_data$events, event_extraction)
bbc_1<-do.call(rbind, bbc_1)

ac <- api_data$audience_categories
audience_categories <- data.frame(audience_code = sapply(ac, function(x) {x$audience_code}), 
                                  audience_name = sapply(ac, function(x) {x$audience_name}),
                                  audience_target_size_hundreds = sapply(ac, function(x) {x$audience_target_size_hundreds}))

bbc_1 <- audience_categories %>% distinct(audience_code, .keep_all= TRUE) %>% 
  inner_join(bbc_1, by = c("audience_code"="audience_code")) %>%
  select(-c(audience_code)) %>%
  mutate(transmission_time_period= lubridate::ymd_hms(transmission_time_period))
head(bbc_1)
```

Inspect the data¶
Checking what is in the data by looking at the average audience size for each audience category and panel

```{r}
bbc_1 %>% select(c(panel_region, audience_name, size_in_hundreds)) %>% pivot_wider(
    names_from = panel_region,
    values_from = c(size_in_hundreds),
    names_vary = "slowest",
    values_fn = "mean"
  )
```
## Age groups watching BBC 1 over a day

Having created the dataframe we can now analyse it in various ways. Here we look at how the audience size changes over the day for various age bands.

```{r}
demog <- bbc_1 %>% filter(audience_name %in% c("Adults 16-34", 
        "Adults 35-44", "Adults 45-54", "Adults 55-64") & 
        panel_region=="BBC Network")
ggplot(demog, aes(x=transmission_time_period, y=size_in_hundreds, color=audience_name)) + geom_line()
```

## How does this vary by region

This might be more interesting if we:

1. Look penetration of the target audience
2. Compare this across the BBC panel regions

```{r, fig.width = 8, fig.height=6}
demog <- bbc_1 %>% filter(audience_name %in% c("Adults 16-34", 
        "Adults 35-44", "Adults 45-54", "Adults 55-64") & 
        grepl("BBC", panel_region)) %>% mutate(audience_penetration = size_in_hundreds/(10*audience_target_size_hundreds))

ggplot(demog, aes(x=transmission_time_period, y=audience_penetration, color=audience_name)) + geom_line() + facet_wrap(vars(panel_region))

```


